\documentclass[letter]{scrartcl}
\usepackage{graphicx}
\usepackage{fullpage} %1in margins
\usepackage{tabularx}
\usepackage{hyperref}

\newcommand{\app}{\sc{393torrent}}

\begin{document}

\title{Requirements for \app}
\subtitle{Dan Keller, Kenneth Link, Nathan McKinley, Ross Nanopoulos}
\date{} % no date

\maketitle

\begin{abstract}
The software requirements specification (SRS) specifies all user stories (i.e. functional requirements) as well as nonfunctional requirements. These requirements are used in iteration planning as well as acceptance testing.  This document should be used by the members of the 393torrent team, who will implement and verify the functionality of the BitTorrent client.
\end{abstract}

\tableofcontents
\pagebreak

\section{Overview}
The BitTorrent client (393torrent) will allow users to download, create, and seed torrent files.  It will enable them to achieve the full functionality of a BitTorrent client in a lightweight form.  The primary objective of this BitTorrent client is to offer a free and open source alternative--without advertisements--to the current heavyweight clients available.  Specific goals of 393torrent can be found in the vision and scope document.

\section{User Stories}
User stories are the functional requirements of XP. They are used in iteration planning as well as acceptance testing.
\\\\
\begin{tabularx}{\textwidth}{X c c c}
\textbf{User Story} & \href{http://c2.com/cgi/wiki?IdealProgrammingTime}{\textbf{Cost (Ideal Days)}}
& \textbf{Status} & \textbf{Iteration} \\
Open .torrent file & & & 1 \\
Communicate with tracker & & & 1 \\
Communicate with peers & & & 1 \\
Track peers \\
Track and assemble file pieces & & & 1 \\
Test piece checksums \\
Calculate percent complete \\
Calcuate download speed \\
Calcuate upload speed \\
Accept --help flag & & & 1 \\
Estimate ETA \\
Display progress bar \\
Output error messages & & & 1 (part) \\
Interpret peer piece request \\
Send file pieces to peer \\
Save state of download to file \\
Resume download from saved state \\
Save state continuously in case process is killed \\
Accept a list of files and output a .torrent \\
Track or store local files being uploaded \\
Download multiple files \\
\href{https://wiki.theory.org/BitTorrentSpecification\#have:_.3Clen.3D0005.3E.3Cid.3D4.3E.3Cpiece_index.3E}{HAVE suppression} \\
\href{https://wiki.theory.org/BitTorrentSpecification\#Queuing}{Queueing} \\
\href{https://wiki.theory.org/BitTorrentSpecification\#Super_Seeding}{Super Seeding} \\
\href{https://wiki.theory.org/BitTorrentSpecification\#Piece_downloading_strategy}{Piece Download Strategy} \\
\href{https://wiki.theory.org/BitTorrentSpecification\#End_Game}{End Game} \\
\href{https://wiki.theory.org/BitTorrentSpecification\#Choking_and_Optimistic_Unchoking}{Choking} \\
Fast Peer extension \\
DHT extension \\
Encryption extension \\
Magnet links \\
Human-readable config file
\end{tabularx}

\section{Nonfunctional Requirements}
Nonfunctional requirements are requirements that do not involve their own coding effort. They are used in acceptance testing, but not iteration planning. 
\subsection{Performance}
\begin{enumerate}
\item Use less than 100 MB of RAM.
\item Make use of available bandwidth, but be functional on a 128 Kbps link.
\item Allow download speeds to spike above disk throughput temporarily.
\end{enumerate}
\subsection{Security}
\begin{enumerate}
\item Never run executable code that the user has asked to download.
\item Fail cleanly on unexpected data, and inform the user of errors.
\end{enumerate}
\subsection{Quality}
\begin{enumerate}
\item Be resilient to network connection failures; be usable over, for instance, a 4G network.
\item Where possible, follow DRY principles.
\item Where possible, use existing libraries.
\item Support "common convention" over strict implementation of protocol.
\end{enumerate}
\pagebreak
\section{Author Contributions}
This section provides the details to what each author contributed to the vision and scope document, as requested per professor Podgurski.
\subsection{Daniel Keller}
Created document outline.
\subsection{Kenneth Link}
\subsection{Nathan McKinley}
Nathan was responsible for the non-functional requirements.
\subsection{Ross Nanopoulos}
Ross created user stories and an overview.

\section{Inspection}
\begin{tabularx}{\textwidth}{X c c}
\textbf{Comment} & \textbf{Reported By} & \textbf{Fixed By} \\
Additional UI features & Ross & Dan \\
Include an overview & Ross & Ross \\
Do not need to include how we will implement features (only what the features are) until design document & Ross & Ross \\
Format user stories the same way & Ross & Ross \\
\end{tabularx}
\end{document}
